---
title: "Homework 1"
author: Alexey Abramov
output: github_document
---

This is my solution to HW1!

##### Loading my libraries

```{r}
library(tidyverse)
library(palmerpenguins)
```

# Problem 1

## Create a dataframe with the specified elements: 

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "low", "mod", "mod", "mod", "high", "high", "high"))
  )
```

## Taking the mean of each variable in my data frame:

```{r}
mean(pull(prob1_df, samp))

mean(pull(prob1_df, samp_gt_0))

mean(pull(prob1_df, char_vec))

mean(pull(prob1_df, factor_vec))
```

##### Comments:
I can take the mean of a numerical and logical vectors, but not the character or factor vectors. 

### Here I am introducing coercion by converting the vectors using the as.numeric call

```{r}
as.numeric(pull(prob1_df, samp))

as.numeric(pull(prob1_df, samp_gt_0))

as.numeric(pull(prob1_df, char_vec))

as.numeric(pull(prob1_df, factor_vec))
```

##### Comments:
Here we can see no change to the numeric vector, while the logical vector was reassigned with 0s and 1s to define the true and false values.  
We were not able to reclassify the character vector to a numeric value. 
However, the factor vector was reassigned to 1, 2, and 3.  Interesting that it started with 2, and not 1?  

### Here we performing mathematical operations on the vectors. 

This markdown has omitted the results.    

```{r echo = T, results = "hide"}

as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp))
```

# Problem 2

## Here is a quick snapshot of the penguins dataset.

```{r exploring penguins}
data("penguins", package = "palmerpenguins")
head(penguins, n=10)
```

### The penguins dataset has these variables:

```{r defining variables in penguins}
names(penguins)
```

### The penguins dataset has 344 rows and 8 columns. 

```{r rows and columns}
nrow(penguins)
ncol(penguins)
```

### Calculating the mean flipper length = 200.9

##### Comments
Got an an error here because there are a few missing values in the data set so I used the na.omit function.  

```{r mean flipper length }
mean(
  na.omit(
    pull(penguins, flipper_length_mm)
    )
  )
```

### Creating a scatterplot of flipper length vs. bill length.

```{r - scatterplot}
ggplot(
  penguins, 
  aes(x = flipper_length_mm, y = bill_length_mm, 
      color = species)) + geom_point()
```

### Saving the scatterplot as a PDF

```{r saving scatter plot}
ggsave("penguins.pdf")
```


