---
title: "Homework 1"
author: Alexey Abramov
output: github_document
---

This is my solution to HW1!

```{r}
library(tidyverse)
library(palmerpenguins)
```

# Problem 1

## Create a df with the specified elements: 

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "low", "mod", "mod", "mod", "high", "high", "high"))
  )
```

## Take the mean of each variable in my data frame:

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

### Comments:
I can take the mean of a numerical and logical vectors, but not the character or factor vectors. 

## Here we are introducing coercion by converting the vectors using the as.numeric command

```{r}
as.numeric(pull(prob1_df, samp))

as.numeric(pull(prob1_df, samp_gt_0))

as.numeric(pull(prob1_df, char_vec))

as.numeric(pull(prob1_df, factor_vec))
```

### Comments
Here we can see no change to the numeric vector, while the logical vector reassigned 0s and 1s to define the true and false values.  We were not able to reclassify the character vector to a numeric value.  However, the factor vector was reassigned to 1, 2, and 3.  Interesting that it started with 2, and not 1?  

## Here we performing mathematical operations on the vectors. 

This markdown with omitted  results.    

```{r echo = T, results = "hide"}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp))
```

# Problem 2

## Here is a quick snapshot of the penguins dataset featuring the first ten rows and columns.  

```{r}
data("penguins", package = "palmerpenguins")
head(penguins, n=10)
```

### The penguins dataset has these variables:
```{r}
names(penguins)
```

### The penguins dataset has 344 rows and 8 columns.  
```{r}
nrow(penguins)
ncol(penguins)
```

### The mean flipper length.  

Got an an error here because there are a few missing values in the data set so I used the na.omit function.  

```{r}
mean(
  na.omit(pull(penguins, flipper_length_mm)
  ))
```

Creating a scatterplot of flipper length vs. bill length.

```{r}
penguins_complete = na.omit(penguins)

pull(penguins_complete, flipper_length_mm)
pull(penguins_complete, bill_length_mm)

ggplot(
  penguins_complete, aes(flipper_length_mm, bill_length_mm)
)
```



